Reconstructing Propositional Proofs in Type Theory

### 2017-11-14 paper/sections/abstract.tex
minor fixes.
[ paper ] minor change in the abstract.

\begin{abstract}
We describe a syntactical proof-reconstruction approach to verify proofs
generated by \Metis prover to problems in classical propositional logic.
To verify these \Metis proofs, we developed a tool able to translate such
derivations to \Agda proof-terms. We formalise in type theory each inference
rule found in \Metis derivations. This allowed us to type-check with \Agda,
\Metis proofs step-by-step. We leave it for future work, the opportunity to
extend this work to support other provers, proof-assistants, and formalisms.

>>>>

\begin{abstract}

We describe a syntactical proof-reconstruction approach to verify proofs
generated by \Metis prover to problems in classical propositional logic. To
verify \Metis proofs, we developed a tool and two Agda libraries able to
translate such derivations to \Agda proof-terms. We formalise in type theory
each inference rule found in the \Metis derivations. This allowed us to type-
check with \Agda, \Metis proofs step-by-step.

% We leave it for future work, the opportunity to
% extend this work to support other provers, proof-assistants, and formalisms.
